### 2020-04-30 thesis/pretext.tex
added in final chapters including author contributions.
wrote author contribution section in thesis.

\justify{}
\doublespacing
This work introduces the development of the novel flat-histogram Monte
Carlo (MC) method SAD and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a variety of physical ‘test’ systems including the 2D Ising model,
square-well fluid, and Lennard-Jones clusters. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all isotherms for any given MOF thereby providing a powerful
way for researchers to determine a MOF’s suitability for gas storage
applications.

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach have tremendously helped me to develop as a scientific
researcher.
I express thanks to my graduate committee members: David McIntyre, Davide Lazzati, Yun-Shik Lee, and GCR Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding graduate students that have positively impacted me (too many to name here but you know who you are).
I would like to acknowledge some of the outstanding undergraduate students
from our research lab that have worked on related research:
Tanner Simpson, Cade Trotter, and Christopher May.
Thank you all for your helpful discussions related to research and life in
general.
Finally, I would like to thank my parents for their unconditional support
throughout my PhD research.

>>>>

\justify{}
\doublespacing
This work introduces the novel flat-histogram Monte
Carlo (MC) method stochastic approximation with a dynamic update factor (SAD) and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a number of physical `test’ systems including the 2D Ising model, a
square-well fluid, and a Lennard-Jones cluster. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all properties of interest for any given MOF thereby providing a powerful way for researchers to determine any porous media's suitability for gas storage applications.

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach to advising have tremendously helped my development as an independent scientific researcher. I express thanks to my entire graduate committee: David McIntyre, Davide Lazzati, Yun-Shik Lee, and graduate council representative Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding undergraduate and graduate students that have positively impacted me personally and professionally while at Oregon State University. Finally, I would like to thank my parents for their unconditional support throughout my Ph.D. research.

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	CONTRIBUTION OF AUTHORS
\end{center}
\justify{}
\doublespacing
Michael A. Perlin worked on much of the early C{}\verb!++! codebase. This codebase was used primarily in the early study of many of the MC methods before switching to RUST. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}. 
Tanner T. Simpson performed many of the early simulations for the flat-histogram methods using the C{}\verb!++! codebase. He also developed using Python some of the plotting scripts that allowed the saved C{}\verb!++! data to be visualized. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}.
Cory M. Simon collaborated together with us on the third manuscript \emph{An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials}. He contributed significantly to the introduction section of the paper and helped in the editing phase throughout preparation. In addition, he designed the first figure in the paper and the first figure in the supplemental to the paper.

### 2020-04-30 thesis/thesis.tex
wrote author contribution section in thesis.

\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte-Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

>>>>

\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
